Analyzing the Impact of Social Attributes on Commit Integration Success

### 2017-03-27 Paper/MSRChallenge2017.tex
tightening through top of eval, and fixing the labels

These social factors are all factors that are tied to a GitHub user's profile
and that are generally correlated with user time and engagement with the site.
Thus, we use them as a proxy for
experience. If we were unable to find information about an author, then we
assigned the commit empty values for these factors.
We also added one item from the MSR Challenge data set, indicating
whether the commit's developer is a core member  
of the associated project. These values were investigated to estimate developers’ experience.

@@

The challenge dataset~\cite{msr17challenge} consists
of commits that date as far back as 2011. The social data we 
gathered is accurate for January 2017. To mitigate the threat of
using future results to predict previous events,
we removed only include data set commits from the years 2014--2016.  Our intuition is
that these social attributes are unlikely to have significant recent changes.

Since we are interested in the success of the job status of each contribution, we 
converted all Travis build statuses to two possible values:
\emph{successful} (passed in the challenge dataset~\cite{msr17challenge}) and \emph{unsuccessful}
(errored, failed, canceled
and started in the original data set). We also condensed all passing and
failing builds in a commit to a single pass or fail for each build status.  If
the commit contained both passing and failing build statuses, we treat it as
both a passing and failed build.

74.43\% of the builds in the reduced dataset were successful, and thus a naive
classifier that always guesses ``successful'' would succeed 74.43\% of the time.
To penalize misclassification for
both classes equally, we created a second balanced dataset by randomly 
sub-sampling the successful builds until the two build status were
equal, through a process known as downsampling. We downsampled the entire
dataset and then trained decision tree classifiers.  We validated the
classifiers with cross-validation. Since the cross-validation is stratified, the
proportion of 50-50 is maintained through the training and testing folds for the
downsampled data. We present results for both
datasets in Section \ref{eval}A,  and only the full dataset for Sections \ref{eval}B and \ref{eval}C.

>>>>

We also added one item from the MSR Challenge data set, indicating
whether the commit's developer is a core member  
of the associated project.
These social factors are all tied to a GitHub user's profile,
and are generally correlated with user time and engagement with the site.
Thus, we use them as a proxy for
experience.  If we were unable to find information about an author, we
assigned empty values to the commit.

@@

The challenge dataset~\cite{msr17challenge} consists
of commits that date as far back as 2011. The social data we 
gathered is accurate for January 2017. To mitigate the threat of
using future results to predict previous events,
we only include commits from the years 2014--2016.  Our intuition is
that these social attributes are unlikely to have significant recent changes.

We converted all Travis build statuses to two possible values:
\emph{successful} (passed in the challenge dataset) and \emph{unsuccessful}
(errored, failed, canceled
or started in the original data set). We also condensed all passing and
failing builds in a commit to a single pass or fail for each build status.  If
the commit contained both passing and failing build statuses, we treat it as
both a passing and failed build.

74.43\% of the builds in the reduced dataset were successful, and thus a naive
classifier that always guesses ``successful'' would succeed 74.43\% of the time.
To penalize misclassification for
both classes equally, we created a second \emph{balanced} dataset by randomly 
sub-sampling the successful builds until the two build status were
equal, through a process known as downsampling. We downsampled the entire
dataset and then trained decision tree classifiers on both.  We validated the
classifiers with cross-validation. Since the cross-validation is stratified, the
proportion of 50-50 is maintained through the training and testing folds for the
downsampled data. We present results for both
datasets in Section~\ref{sec:successClassification},  and only the full dataset for Sections~\ref{sec:core} and \ref{sec:followerSuccess}.
